\section{Test of the converters}
In this part, all the requirements related to the converters will be tested if they are fulfilled. 


\subsection{Test of requirement \autoref{req:ADC_resolution}}
According to \autoref{req:ADC_resolution}, the \gls{adc} must have a resolution of at least 10 bits. In \autoref{sec:dsp_description} it is seen that the TMS320C5515 eZdsp development board has an \gls{adc} with a resolution of \SI{92}{\decibel} (16-bits). Thus the requirement is fulfilled.  

\subsection{Test of requirement \autoref{req:ADC_Fs}}
According to \autoref{req:ADC_Fs}, the \gls{adc} must have a sampling frequency of at least \SI{8.8}{\kilo\hertz}. In \autoref{sec:dsp_description} it is seen that the TMS320C5515 eZdsp development board has an \gls{adc} with a sampling frequency, which can be set from \SI{8}{\kilo\hertz} to \SI{192}{\kilo\hertz}. Thus the requirement is fulfilled.

\subsection{Test of requirement \autoref{req:DAC_resolution}}
According to \autoref{req:ADC_resolution}, the \gls{dac} must have a resolution of at least 10 bits. In \autoref{sec:dsp_description} it is seen that the TMS320C5515 eZdsp development board has a \gls{dac} with a resolution of \SI{100}{\decibel} (17-bits). Thus the requirement is fulfilled.  

\subsection{Test of requirement \autoref{req:DAC_Fs}}
According to \autoref{req:ADC_Fs}, the \gls{adc} must have a sampling frequency of at least \SI{8.8}{\kilo\hertz}. In \autoref{sec:dsp_description} it is seen that the TMS320C5515 eZdsp development board has a \gls{dac} with a sampling frequency, which can be set from \SI{8}{\kilo\hertz} to \SI{192}{\kilo\hertz}. Thus the requirement is fulfilled.
 

