
\section{Quality}

The bandwidth in an analog sound signal can be increased infinitely unlike the digital one where it is limited by the sampling rate that is being used. \\
The \gls{snr} is higher in digital signals than analog ones because of their low bit depth. The bit depth is a variable that takes into account the change in amplitude between each sample. If the sample rate is not high enough in digital signal, the \gls{snr} is higher \citep{analog_quality}. The quantization noise do exist in digital signal and not in analog ones, the same goes for aliasing \citep{analog_aliasing}. \\
Some will argue that by sufficiently increasing the sampling rate, the quality difference between analog and digital sounds can no longer be felt \citep{analog_storage}.

\section{Mobility}

Digital Sounds are more portable than analog ones, they can be played on different machines and copied without losing any information unlike the analog sound that can only be played on a tape for instance \citep{analog_quality}. 

\section{Lifetime}

A digital sound can last longer than an analog one. A Vinyl disk for example can get damaged and impact the sound stored on it and thus the quality. On the other side, a digital file saved on a computer cannot get damaged physically, unless the storage does, and can be duplicated very easily to preserve it. With the rise of cloud systems, the loss of a digital file is nearly impossible unless intentional \citep{analog_storage}.


\section{Requirements}

It is easier to fulfill given requirements using digital over analog signal processing because the user has more control over the digital controller than the analog one. If at anytime, the engineer realizes that the components needs more processing power, it can be easily upgraded \citep{analog_requirements}.

\section{Functionality and Customization}

With only one \gls{dsp}, it possible to program numerous effects, personalize them and even create custom ones. The process is also not complicated if there is a coded scripts that does the \gls{dsp} programing job for the end-user. Effects presented in \autoref{sec:effects} are just part of a growing and endless world of digital pedals. 

 